Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-06 paper/paper.tex
Corrections of Box 2 experiments

\item Experiment (Humans): We hypotherize that time horizon should be modulated by different factors such as age, stress, and impulsivity. Using a temporal discounting task, we can measure how the time horizon could be affected at the behavioral level, and then trace back its potential representation at the neural level. Experimental design can be between groups (by age or with a impulsive population like chronic gamblers or drug addicts), or within group using a stress.

@@

\item Experiment (Animals): how synaptic epigenesis between DMN nodes can form a neural correlate of the policy matrix update? % Simulations:

>>>>

\item Experiment (Humans): We hypothesize that the relevant time horizon is modulated by various factors such as organism age, acute stress, and time-enduring impulsivity traits. Using a temporal discounting experiment, it can be measured how the time horizon could be affected at the behavioral level, and then trace back its potential representation at the neural level. The experiment can be designed to examine between-group (by age or with a impulsive population like chronic gamblers or drug addicts) and within group effects using a stress; and brought in context with the participant’s age and impulsivity tendencies.

@@

\item Experiment (Humans \& Animals): An additional layer of learning concerns the addition of new entries in the table (i.e., state and action). The framing of the policy matrix is not described here but could be supported by synaptic epigenesis \citep{gisiger_acquisition_2005}. Indeed, the tuning of synaptic weights through learning can stabilize additional patterns of activity by creating new attractors in the neural dynamics landscape \citep{takeuchi_synaptic_2014}. Those attractors will then constrain both the number of factors taken into account by decision processes and the number of behaviors at reach by the agent \citep{wang_decision_2008}. To probe this aspects, we propose two experiments probing how synaptic epigenesis forms a neural correlate of the policy matrix update: one in human, investigating the changes of functional connectivity between DMN nodes following a temporal discounting experiment; the second in rodents, directly testing with anterograde tracing how homolog regions of the DMN present increased synaptic changes compare to other brain regions.
